A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-03 Simulator/article.tex
Started on journal version of simulator

%===============%                               %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
% DOCUMENTCLASS %                                See full option description in "mytemplate.cls"
%===============%                               %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%

\documentclass[
   UAM                                          % Document type (non-standard)
 , 12pt                                         % Text size
%  , draft
%  , final                                        % Quality
%  , xelatex                                      % Use the XeLaTeX compiler
%  , biblatex                                     % Use 'biblatex' for references (best by far)
 , bibtex                                       % Use 'bibtex' for references (oldschool :)
%  , movie
%  , notodos                                      % Disable todos
 , layout
%  , defaultformat                                % Attempt to use default formatting options
%  , glossary                                     % Use a glossary
]{common/mytemplate}
% \bibliography{references}
\hypersetup{
   bookmarksopen=true
 , bookmarksopenlevel=2
}

\definecolor{tabBlue}{HTML}{AACCFF}
\newlength\oldparindent
\setlength\oldparindent{\parindent}

\newlength\figwidth
\setlength\figwidth{0.7\linewidth}

% \setlength\floatsep{\baselineskip}
\setcounter{topnumber}{1}
% \setlength\baselineskip{12pt}
% \selectfont

@@

@@

% \usepackage{caption}
\usepackage{subcaption}
\usepackage{color}

% Tune floats
\renewcommand{\topfraction}{0.9}  % max fraction of floats at top
\renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{1}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.85}  % require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.85} % require fuller float pages

\begin{document}
% Load the references.bib file
% \bibliography{../../../library.bib}

\pagestyle{plain}
% \layout
% \printinunitsof{cm}
% \prntlen{\baselineskip}
% \the\textwidth
% \the\linewidth
% \prntlen{\textwidth}\\
% \prntlen\linewidth\\
% \prntlen\oddsidemargin\\
% \prntlen\oddsidemargin
% \newpage

\title{A GPU Sonar Simulator for Automatic Target Recognition}%
%
\author{Jo Inge Buskenes\firstAddress, Herman Midelfart\secondAddress, \O{}ivind Midtgaard\secondAddress}%
%
\begin{contact}
  \firstAddress Dept. of Informatics, P.O.Box 1080 Blindern, N-0316 OSLO\\
  \secondAddress Norwegian Defence Research Establishment (FFI) P.O.Box 25, NO-2027 Kjeller
\end{contact}%
%
\begin{contact}
Contact author: Jo Inge Buskenes\\
Dept. of Informatics, Univ. of Oslo, P.Box 1080 Blindern, N-0316 OSLO\\
\href{mailto:joibu@ifi.uio.no}{joibu@ifi.uio.no}
\end{contact}%
%
\begin{abstract}
Template matching is a common technique for automatic classification of objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing the object of interest, correlate it with a set of template images, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a representative set of template images covering the relevant configurations of object and seabed.

We target this challenge with a sonar simulator that first takes as input a seabed model derived from the real sonar image. Then it places a 3D object model on the seabed, renders the scene, and adds the resulting image to the template set. For every object type, position, alignment and material, the procedure is repeated, and a correlation coefficient computed. The best performance is obtained when these parameters are estimated from the sonar image as part of the classification process. The simulator is therefore written in OpenGL and OpenCL and runs on graphics processing units (GPUs). The result is a fast performing and portable on-the-fly template generator which can adapt to the characteristics of the current scene.
\end{abstract}%
%
\keywords{Sonar, SAS, simulator, template matching, OpenGL, OpenCL}

@@

\section{Conclusion}

@@

% 
% 
% \begin{itemize}
% \item Mer testing
% \item Robustifisering
% \item Tuning
% \end{itemize}
%

% Ligger nesten med kortsiden til.
% Bilde og templat segmenteres hver for seg.
% Ikke adaptiv - darlig. Feil lengde, skyggen for kort (synket). Orientering feil. Feil spacing. 
% Adaptiv - malt objekt. Passer bra. 
% 
% Videre:
% - Mer testing
% - Robustifisering
% - Tuning

% 
\bibliography{references}
% \bibliography{../../../library.bib}
% 
% % If biblatex (file is loaded in preamble):
% % \printreferences

>>>>

%%%%%%%%%%%%%%%%                                ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% CONDITIONALS %
%%%%%%%%%%%%%%%%                                ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\newif\ifPeerReview\PeerReviewfalse              % Whether to create the PeerReview version or
                                                % Journal version
\newif\ifOnlineColor\OnlineColortrue            % Compile online color version?

\newif\ifFlatArchive\FlatArchivefalse           % Whether archive is flat (messy) or contain 
                                                % subfolders for graphics etc.
\newif\ifFloatAtEnd\FloatAtEndfalse             % Available in PeerReview mode:
                                                % Place floats at end of document?
\newif\ifTODO\TODOtrue                        % Use todo notes?

\ifOnlineColor
   \newcommand\figPostfix{_online}              % Colored images online
\else
   \newcommand\figPostfix{_bw}                  % Black and white in journal
\fi

%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% IEEEtran %
%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\ifPeerReview
\documentclass[12pt,journal,draftclsnofoot,onecolumn]{IEEEtran}
% \newcommand\CLASSINPUTbaselinestretch{1.66}     % http://theoval.cmp.uea.ac.uk/~nlct/latex/thesis/node17.html
\else
\documentclass[journal]{IEEEtran}
\fi

% \RequirePackage[latin1]{inputenc}%              % Set input encoding (optionally latin1)
% \RequirePackage[T1]{fontenc}%                 % Set font encoding
% \usepackage[norsk]{babel}

% Single column review mode:
%\documentclass[12pt,journal,onecolumn]{IEEEtran}
%\newcommand\CLASSINPUTbaselinestretch{2}
%\RequirePackage{calc}
%\RequirePackage{fp} 
% Left margin = 1 inch + hoffset + oddsidemargin (or evensidemargin)
% Adding the 2cm gutter width to the odd/even side margins:
%\setlength\hoffset{0pt}
%\setlength\oddsidemargin{4cm}       % 4cm margins on the left side
%\addtolength\oddsidemargin{-1in}    % Subtract the initial 1 inch
%\setlength\textwidth{21cm-8cm}    % A4 width (21cm) minus margins on either side

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% IEEE ''APPROVED'' PACKAGES %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\usepackage{cite}

\ifCLASSINFOpdf
   \usepackage[dvips]{graphicx}                 % Might not work. Use 'latex' instead of 
   \ifFlatArchive\else                          % 'pdflatex'
      \graphicspath{./gfx/}
   \fi
\else
   \usepackage[dvips]{graphicx}
   \ifFlatArchive\else
      \graphicspath{./gfx/}
   \fi
\fi

\RequirePackage[table,dvipsnames,svgnames]{xcolor}

\usepackage[cmex10]{amsmath}                    % cmex10 option to be IEEE explore compliant
\interdisplaylinepenalty=2500                   % Allows multiline equations to be broken

% \RequirePackage{amssymb}

\RequirePackage{array}
% 
% \ifCLASSOPTIONcompsoc
%    \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \else
%    \usepackage[caption=false,font=footnotesize]{subfig}
% \fi

% \usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\usepackage{calc}
\usepackage{fp}

% 
% \ifCLASSOPTIONcaptionsoff                       % IEEE promoted hack to turn off captions from the 
%    \let\MYorigsubfloat\subfloat                 % subfloat package should the captionsoff option
%    \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}} % be specified.
% \fi

\ifFloatAtEnd
\ifCLASSOPTIONcaptionsoff                       % Places float at the end of the document when the
  \usepackage[nomarkers]{endfloat}              % captionsoff options is specified to IEEEtrans.cls
  \let\MYoriglatexcaption\caption               % (PeerReview mode)
  \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
\fi
\fi

\usepackage{fixltx2e}                           % Fix some twocolumn float problems

%\usepackage{stfloats}                          % Allows: \begin{figure*}[!b]
                                                % (double column figures on top/bottom)

\usepackage{url}                                % Support for handling and breaking URLs

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
pdftitle={An Optimized GPU Implementation of the MVDR Beamformer for Active Sonar Imaging},
pdfsubject={},
pdfauthor={Jo Inge Buskenes},
pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
   \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

%%%%%%%%%%%%%%%%%%%%%%%                         ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% ADDITIONAL PACKAGES %       
%%%%%%%%%%%%%%%%%%%%%%%                         ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \ifPeerReview
% \let\OldIncludegraphics{\includegraphics}
% \usepackage{letltxmacro}
% \LetLtxMacro{\OldIncludegrsaphics}{\includegraphics}
% \renewcommand{\includegraphics}[2][]{\OldIncludegraphics[width=\linewidth, #1]{#2}}
% \fi

% % \makeatletter
% % \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
% % \else\Gin@nat@width\fi}
% % \makeatother
% % \let\Oldincludegraphics\includegraphics
% % \renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage[maxfloats=40]{morefloats}
\newcounter{todoidx}
% \setcounter{todoidx}

\ifTODO
   \definecolor{todobackground}{rgb}{0.95,0.95,0.95}
   \setlength\marginparsep{1pt}
   \setlength\marginparwidth{35pt}
   \newlength\marginparwidthsmall
   \setlength\marginparwidthsmall{\marginparwidth}
   \addtolength\marginparwidthsmall{-7pt}
   \newcommand\todo[1]{%
      \addtocounter{todoidx}{1}%
      {\color{Red}\bf(\thetodoidx{})}%%\fbox{\bf\thetodoidx{}}}%
      \marginpar{%
         {\vspace*{-10pt}\color{Red}\fbox{\bf\thetodoidx{}}}\\%
         \fcolorbox{red}{todobackground}{\parbox{\marginparwidthsmall}{\scriptsize #1}}}}

   \newcommand\todopar[1]{\fcolorbox{red}{white}{\parbox{0.97\linewidth}{#1}}}
\else
%    \usepackage[disable]{./todonotes} 
   \newcommand\todo[1]{}
\fi

\newenvironment{narrow}[2]{%
\begin{list}{}{%
\setlength{\topsep}{0pt}%
\setlength{\leftmargin}{#1}%
\setlength{\rightmargin}{#2}%
\setlength{\listparindent}{\parindent}%
\setlength{\itemindent}{\parindent}%
\setlength{\parsep}{\parskip}}%
\item[]}{\end{list}}

\usepackage{float}

\ifOnlineColor
   \definecolor{tabBlue}{HTML}{AACCFF}
\else
   \definecolor{tabBlue}{HTML}{CCCCCC}
\fi

%%%%%%%%%%                                      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% MACROS %       
%%%%%%%%%%                                      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\newcommand\graphicsAI[2][]{%
  \immediate\write18{./bin/laFigure #2 #1}%
  \input{result}}%

% \DeclareMathOperator*{\argmin}{\text{arg}\;\text{min}}

\newcommand\Fig[1]{Fig.~\ref{#1}}

\newcommand\Grey[1]{{\color{Grey}#1}}
\newcommand\Red[1]{{\color{Red}#1}}
\newcommand\Blue[1]{{\color{Blue}#1}}
\newcommand\DarkBlue[1]{{\color{DarkBlue}#1}}
\newcommand\LightBlue[1]{{\color{LightBlue}#1}}
\newcommand\Brown[1]{{\color{Brown}#1}}
\newcommand\Green[1]{{\color{Green}#1}}
\newcommand\SeaGreen[1]{{\color{SeaGreen}#1}}
\newcommand\Yellow[1]{{\color{yellow}#1}}
\newcommand\Orange[1]{{\color{orange}#1}}

\newcommand\nn{\nonumber\\}

\newcommand\nmat[1]{\begin{matrix}#1\end{matrix}}
\newcommand\bmat[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand\case[1]{\begin{cases}#1\end{cases}}
\newcommand\textbox[2]{\footnotesize\text{\parbox{#1}{\centering\emph{#2}}}}

\newcommand\rand{\text{rand}}
\newcommand\randn{\text{randn}}
\newcommand\rect{\text{rect}}
\newcommand\sinc{\text{sinc}}
\newcommand\tr{\text{tr}}
\newcommand\adj{\text{adj}}

% \newcommand\max{\text{max}}
\newcommand\argmin[1]{\text{arg}\;\underset{#1}{\text{min}}}

\newcommand\qqquad{\quad\qquad}
\newcommand\qqqquad{\qquad\qquad}

% \renewcommand\l[1]{\left#1}
% \renewcommand\r[1]{\right#1}

% {\text{\parbox{1.5cm}{\centering volume hyper- sphere}}}

%Keyword colouring:
\newcommand\kw[1]{#1}
\newcommand\parm[1]{#1}%\color{Black}#1\color{Black}}

\newcommand\of[1]{\scriptstyle(\parm{#1})\displaystyle}
\newcommand\df[1]{\scriptstyle[\parm{#1}]\displaystyle}
\newcommand\var[3]{#1_\text{#2}\of{#3}}

\newcommand\diag{\text{diag}}

% \raisebox{lift}[extend-above-baseline][extend-below-baseline]{text}
\newcommand\mt[1]{\text{\emph{#1}}} %mt = mathtext
\newcommand\mathnorm{\textstyle}
\newcommand\mathbig[1]{\displaystyle#1\mathnorm}
\newcommand\mathsmall[1]{\scriptstyle#1\mathnorm}
\newcommand\mathtiny[1]{\scriptscriptstyle#1\mathnorm}
\newcommand\sfrac[2]{\scriptstyle\raisebox{0.25pt}[0pt][0pt]{$\frac{#1}{#2}$}\mathnorm}
\newcommand\nfrac[2]{\textstyle\frac{#1}{#2}\displaystyle}

\newcommand\sumu[1]{\sum\limits^{#1}\;}
\newcommand\suml[1]{\sum\limits_{#1}\;}
\newcommand\sumb[2]{\sum\limits_{#1}^{#2}\;}

\newcommand\produ[1]{\prod\limits^{#1}\;}
\newcommand\prodl[1]{\prod\limits_{#1}\;}
\newcommand\prodb[2]{\prod\limits_{#1}^{#2}\;}

\newcommand\defeq{\overset{\underset{\mathrm{def}}{}}{=}}

%Math macros:
\newcommand\T{^{\scriptscriptstyle T}}
\renewcommand\H{^{\scriptscriptstyle H}}

@@

\newcommand\Om{O_\text{m}}
\newcommand\Oa{O_\text{a}}
\newcommand\Nl{N_\text{l}}
\newcommand\Nk{N_\text{k}}
\newcommand\1{\vec 1}
\newcommand\I{\mat I}
\renewcommand*\a{\vec a}
\renewcommand*\i{\vec i}
\renewcommand*\k{\vec k}
\newcommand*\n{\vec n}
\newcommand*\p{\vec p}
\newcommand*\s{\vec s}
\newcommand*\w{\vec w}
\newcommand*\x{\vec x}
\newcommand*\y{\vec y}

\newcommand*\A{\mat A}
\newcommand*\B{\mat B}
\newcommand*\C{\mat C}
\newcommand*\E{\mat E}
\renewcommand*\P{\mat P}
\newcommand*\eP{\mat{\hat P}}
\newcommand*\R{\mat R}
\newcommand*\Ri{\R^{-1}}
\newcommand*\eR{\mat{\hat R}}
\newcommand*\eRi{\hat{\mat R}\;\!^{-1}}
\newcommand*\Navg{N_\text{avg}}
\newcommand*\W{\mat W}
\newcommand*\X{\mat X}
\newcommand*\Xd{\X_{\!\Delta}}
\newcommand*\Y{\mat Y}

@@

\renewcommand*\L{\mat \Lambda}
\newcommand*\U{\mat U}
% \renewcommand*\t{\mathtiny{^T}}
% \newcommand*\h{\mathtiny{^H}}
\renewcommand*\t{^T}
\newcommand*\h{^H}

\usepackage{tikz}
\usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}
% \usepackage{datatool}
% \usepackage{glossaries}

\newenvironment{outline}
{\begin{itemize}}
{\end{itemize}}

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% GLOSSARY %
%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \makeglossaries
% \input{../../Library/glossary}

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \usepackage{yfonts}

% \graphicspath{submission/final/gfx/}

\begin{document}

\title{A GPU Sonar Simulator for Automatic Target Recognition}

\author{{Jo~Inge~Buskenes,~\IEEEmembership{Student Member,~IEEE,} %
        Herman~Midelfart, %
        \O{}ivind~Midtgaard} %
\thanks{J. I. Buskenes is with the Department of Informatics, University of Oslo, Norway.}%
\thanks{H. Midelfart and \O. Midtgaard are with The Norwegian Defence Research Establishment (FFI), Norway.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2005; revised January 11, 2007.}
}

% The paper headers
\markboth{IEEE Journal of Oceanic Engineering}%
{A GPU Sonar Simulator for Automatic Target Recognition}

% Publishers ID mark:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
Template matching is a common technique for automatic classification of objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing the object of interest, correlate it with a set of template images, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a representative set of template images covering the relevant configurations of object and seabed.

We target this challenge with a sonar simulator that first takes as input a seabed model derived from the real sonar image. Then it places a 3D object model on the seabed, renders the scene, and adds the resulting image to the template set. For every object type, position, alignment and material, the procedure is repeated, and a correlation coefficient computed. The best performance is obtained when these parameters are estimated from the sonar image as part of the classification process. The simulator is therefore written in OpenGL and OpenCL and runs on graphics processing units (GPUs). The result is a fast performing and portable on-the-fly template generator which can adapt to the characteristics of the current scene.
\end{abstract}

% Keywords (normally not used for peer reviews)
\ifPeerReview\else
\begin{IEEEkeywords}
Sonar, SAS, simulator, template matching, OpenGL, OpenCL.
\end{IEEEkeywords}
\fi}
% \fi

% make the title area
\maketitle

% This command fixes abstract positioning for compsoc articles:
\IEEEdisplaynotcompsoctitleabstractindextext

% (Optional) Add some extra info on cover page of peer review papers:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi

% Insert page break and insert second title (peer review mode)
\IEEEpeerreviewmaketitle

\maketitle

@@

\section{Conclusion}\label{conclusion}

@@

% \appendices
% 
% \section{MVDR Complexity Formulas}\label{mvdr_formulas}
% 
% \section{GPU Throughput}\label{throughput}
% 
% bs bs

% use section* for acknowledgement
\ifCLASSOPTIONcompsoc% % This command fixes abstract positioning for compsoc articles:
% \IEEEdisplaynotcompsoctitleabstractindextext
% 
% % (Optional) Add some extra info on cover page of peer review papers:
% % \ifCLASSOPTIONpeerreview
% % \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% % \fi
% 
% % Insert page break and insert second title (peer review mode)
% \IEEEpeerreviewmaketitle
% 
% 
%

  \section*{Acknowledgments}
\else
  \section*{Acknowledgment}
\fi

The authors would like to thank the Norwegian Defence Research Establishment (FFI) for funding to develop the simulator\todo{more?}.

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\bibliographystyle{IEEEtran}
\bibliography{references}

% Generated by IEEEtran.bst, version: 1.13 (2008/09/30)
% \begin{thebibliography}{10}
% stuff here
% \end{thebibliography}

\input{bio/jo_inge_buskenes}
% \input{bio/jon_petter_aasen}
% \input{bio/carl-inge_nilsen}
% \input{bio/andreas_austeng}

% 
% IMAGE METRICS
%
% - Point spread function (res via main lobe width, SAS gain via PDF height)
% - Constrast measures
%
% ACR = cL/2
% C = (s+n)/n ratio
% - 
% WHO's needing processing power
% - Centre for Maritime Research and Experimentation

\vfill
